### 2025-09-29 src/articles/article12.qmd
remove redundant backslashes

1. If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council ({{< var acronyms.ec >}}) position, that at-large member is immediately removed from office.
1. Any At-Large Member may be removed for the following reasons:
   a. Failure to perform their duties, including unexcused absence from more than one board meeting per semester.
   a. Failure to maintain confidentiality of all proceedings of the board.\
   a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
   a. At-large members can only be removed by an {{< var glossary.absolute-supermajority >}} vote of the active chapter ({{< var acronyms.ibl >}} Article V, Section 22(e)).

@@

1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
   a. The possible pleas are {{< var glossary.responsible-plea >}}, {{< var glossary.not-responsible-plea >}}, and {{< var glossary.no-contest-plea >}}.\
   a. If a plea is not received within the twenty-four hours specified above, a {{< var glossary.no-contest-plea >}} will be entered.

>>>>

1. If, at any time, an at-large member becomes ineligible to hold office or is elected to an Executive Council ({{< var acronyms.ec >}}) position, that at-large member is immediately removed from office.
1. Any At-Large Member may be removed for the following reasons:
   a. Failure to perform their duties, including unexcused absence from more than one board meeting per semester.
   a. Failure to maintain confidentiality of all proceedings of the board.
   a. Conduct unbecoming of an at-large member or which negatively affects the credibility of the board.
   a. At-large members can only be removed by an {{< var glossary.absolute-supermajority >}} vote of the active chapter ({{< var acronyms.ibl >}} Article V, Section 22(e)).

@@

1. Upon receiving the notification, the accused has twenty-four hours to submit a plea in writing to the Vice President.
   a. The possible pleas are {{< var glossary.responsible-plea >}}, {{< var glossary.not-responsible-plea >}}, and {{< var glossary.no-contest-plea >}}.
   a. If a plea is not received within the twenty-four hours specified above, a {{< var glossary.no-contest-plea >}} will be entered.

### 2025-09-29 src/articles/article5.qmd
remove redundant backslashes

1. For each elected position the election will proceed as such:
   a. For each candidate:
      i. Candidates will be allowed speeches following these rules:
         1. Other candidates will leave the room.
         1. Candidates will be allowed not less than three minutes to speak.
      i. The chapter will be allowed to ask the candidate questions following these rules:
         1. The chapter will be allowed not less than two minutes to question.
         1. Any time not used by a candidate for his speech will be allowed for questions.
   a. The chapter will discuss the candidates subject to the following rules:
      i. All candidates will leave the room.
      i. The chapter will be allowed not less than five minutes to discuss.
      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.\
   a. Pledges will be allowed to vote in the election in direct exception to the above @sec-art-GW6C9D29, Item 2.

@@

1. Vice President
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix as outlined in @sec-art-Q8OV40FK.
   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in @sec-art-C89656BJ.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in @sec-art-YOSPIQLS.
   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).\
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in @sec-art-VI2T9PVL, Item 3a. o. Must live in the house.

@@

1. Treasurer
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother which includes all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.\
   a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election. A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate. This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter. Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Scholarship Chair
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph i.
   a. Performs all duties specified by the Greek Life Office, {{< var acronyms.ifc >}}, and the University.
   a. Will prepare a written scholarship program, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:\
      i. A plan for the creation of Scholarship contracts for all brothers.
      i. A plan for ensuring the chapter house is an environment conducive to studying.
      i. A plan for providing incentives for academic achievements.
   a. Will present the scholarship program to new members.
   a. Works with the Marshal to promote academic well-being among New Members.
   a. Organizes a formal scholarship dinner to recognize achievement about scholarship within the chapter.
   a. Will arrange at least one program per semester with a speaker who will talk to the chapter about scholarship or an issue relating to scholarship.
   a. Will ensure all brothers are part of at least one non-greek club or activity.
   a. {{< var glossary.attend >}}s monthly meetings with the Greek Community Educational Consultants in accordance with Case Western Reserve University ({{< var acronyms.cwru >}}) Greek {{< var glossary.community-standards >}}.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Historian
   a. Performs all duties stated in the I{{< var acronyms.ibl >}}BL Article V, Section 6, paragraph h.
   a. Assists alumni relations chair with the alumni database.\
   a. Ensures that pictures are taken at chapter events.
   a. Will make a yearly scrapbook for the year that they serve, with assistance from the previous historian.
   a. Manages the chapter's online photo and video galleries jointly with the Public Relations Chair.
   a. Works with the house manager to ensure that composites are displayed correctly.
   a. Maintains and updates the photos around the house.
   a. Maintains the chapter museum.

@@

1. Alumni Relations Chair\
   a. Collects materials for and edits the Alumni Newsletter with the help of the Alumni Corporation and sends out the Alumni newsletter before the last day of classes.
   a. Maintains the alumni database.
   a. Serves as chair of the Alumni Relations Committee.
   a. Organizes the Alumni Ceremony at the end of the semester in which they serve.
   a. Plans the annual OX Roast event with the alumni to be held in the fall semester.
   a. Will be appointed after OX Roast to serve until the next OX Roast.
   a. Serves as a member of {{< var acronyms.ccc >}}.

@@

1. Food Steward
   a. Works with a chef or catering service to maintain a brotherhood meal plan.\
   a. Ensures the service chosen for the meal plan is paid for according to the agreement with the chef or catering service.
   a. Must be on the meal plan.
   a. Works with the Detail Manager to keep public areas in the kitchen clean and ensure proper storage of food.
   a. Assigns cabinet and fridge space to in-house brothers.
   a. Must live in the house.

@@

1. Voting
   a. Voting Members
      i. Vice President
      i. Vice President of Health and Safety\
      i. Secretary
      i. Treasurer
      i. Marshal
      i. Recruitment Chair
      i. Scholarship Chair
   a. {{< var glossary.quorum >}} will consist of at least five members, at least four of whom must be voting members. c. All votes are decided by an {{< var glossary.absolute-majority >}} of {{< var acronyms.ec >}}.
      i. The President will have a vote in case of a tie.

@@

1. The chapter will have the following groups of committees:
   a. Standard Committees
      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
         1. Alumni Relations Committee and Member Development Committee
         1. Health and Safety Committee and Scholarship Committee
         1. Philanthropy and Service Committee and Social Committee
         1. Public Relations Committee and Recruitment Committee
      i. All Standard committees will do the following:
         1. Meet at least once every two weeks as directed by their chair.
            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1. Assist the chair in the discharge of their duties.
         1. Create a set of goals for the committee at the first meeting of the committee.
         1. Work toward the goals of the committee.
   b. Operational Committees\
      i. Ad hoc committees
         1. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1. Purpose and Duties
            a. To create a budget for the chapter for the next year pursuant to @sec-art-GD7C1K2U.
            a. To examine any financial issues of the chapter.
         1. Membership
            a. The Treasurer will serve as chair of the Budget Committee.
            a. The body of the committee will be selected by the Treasurer.
         1. Procedure
            a. The committee will be created and convened during the budgeting process outlined in @sec-art-GD7C1K2U, Item 3.
            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
      i. Committee Chair Committee ({{< var acronyms.ccc >}})
         1. Purpose
            a. To facilitate communication between committee chairs.
            a. To keep the Vice President informed of committee business.
            a. To help the Vice President ensure that committees are performing all necessary duties.
         1. Membership
            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
            a. The chairs of all Standard Committees will be members.
            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
         1. Procedure
            a. The committee will meet at least once every two weeks while school is in session.
            a. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1. The Mandatory Bylaw Revision Committee will function in accordance with @sec-art-YOSPIQLS.

>>>>

1. For each elected position the election will proceed as such:
   a. For each candidate:
      i. Candidates will be allowed speeches following these rules:
         1. Other candidates will leave the room.
         1. Candidates will be allowed not less than three minutes to speak.
      i. The chapter will be allowed to ask the candidate questions following these rules:
         1. The chapter will be allowed not less than two minutes to question.
         1. Any time not used by a candidate for his speech will be allowed for questions.
   a. The chapter will discuss the candidates subject to the following rules:
      i. All candidates will leave the room.
      i. The chapter will be allowed not less than five minutes to discuss.
      i. If the candidate is elected by white {{< var glossary.ballot >}}, this section does not apply.
   a. Pledges will be allowed to vote in the election in direct exception to the above @sec-art-GW6C9D29, Item 2.

@@

1. Vice President
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph b.
   a. Serves as Parliamentarian for the chapter and is {{< var glossary.responsible >}} for all committees.
   a. Maintains the chapter's local bylaws.
   a. Ensures legislation records are up to date.
   a. Adds all permanent legislation to the appropriate appendix as outlined in @sec-art-Q8OV40FK.
   a. Adds {{< var acronyms.ec >}} Interpretations to the Appendices.
   a. Appoints active members to committees at the beginning of each semester.
   a. Assigns living space as outlined in @sec-art-C89656BJ.
   a. Fills out Greek Life and International Headquarters ({{< var acronyms.ihq >}}) awards that are due in their term.
   a. Serves as chair of the Bylaw Revision Committee as outlined in @sec-art-YOSPIQLS.
   a. Serves as chair of {{< var acronyms.ec >}} and represents it to the chapter.
   a. Serves as chair of the Committee Chair Committee ({{< var acronyms.ccc >}}).
   a. Serves as chair of Standards Board.
   a. May make Ad Hoc Committees at their discretion as defined in @sec-art-VI2T9PVL, Item 3a. o. Must live in the house.

@@

1. Treasurer
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph e.
   a. Is accountable to the Alumni Corporation.
   a. Collects all feeds, dues, and fines.
   a. Records all transactions made by the chapter.
   a. Will provide a written report at the request of any brother which includes all payments paid out, all monies received, current bank account balances, and budget updates.
   a. Keeps private all individual account balances except from the brother whose account it is and {{< var acronyms.ec >}}.
   a. Issues enumerated bills for all brothers and New Members at least three times a semester unless otherwise decided by the chapter.
   a. Announces the names of all members on {{< var glossary.financial-probation >}} at each chapter meeting during the Treasurer's Report or before any vote, whichever occurs first.
   a. Will create a budget following the process outlined in @sec-art-GD7C1K2U.
   a. Ensures compliance with the General Rules for chapter finances outlined in @sec-art-SKY8T9UM.
   a. Will propose a housing contract to the chapter by the last chapter meeting of each semester with a final version to be approved at the first chapter meeting of the next semester.
   a. Will ensure that all brothers living in the house have signed a housing contract by the second chapter meeting of each semester.
   a. Maintains an emergency fund of no less than $3000 and can withdraw money from the fund only with the authorization of two of the three highest officers.
   a. Will meet with the Alumni Financial Advisor at least twice each semester.
   a. Will file taxes at least two weeks before the filing deadline each year.
   a. Will ensure that taxes will be reviewed by the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}} no later than one month before the filing deadline.
   a. Will send taxes by certified mail, and will distribute this certification to the {{< var acronyms.cab >}} financial advisor, alumni housing corporation financial advisor, and {{< var acronyms.ec >}}.
   a. Will retain a physical and electronic backup of financial records for no fewer than five years.
   a. Maintain a changelog of the budget.
   a. Give a monthly financial report to the chapter and deliver the report to {{< var acronyms.cab >}}.
   a. The Treasurer cannot be elected or appointed to a position which has permission to spend from the budget.
   a. Cannot be elected to another position during their term.
   a. A candidate for the position of Treasurer must be interviewed by the {{< var acronyms.cab >}} prior to the election. A {{< var glossary.simple-majority >}} vote of the {{< var acronyms.cab >}} may veto that candidate. This veto can be overruled by a {{< var glossary.supermajority >}} vote of the chapter. Failure for {{< var acronyms.cab >}} to meet with a candidate prior to elections will be interpreted as {{< var acronyms.cab >}} waiving their right to interview the candidate.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Scholarship Chair
   a. Performs all duties stated in the {{< var acronyms.ibl >}} Article V, Section 6, paragraph i.
   a. Performs all duties specified by the Greek Life Office, {{< var acronyms.ifc >}}, and the University.
   a. Will prepare a written scholarship program, submit it to the Office of Greek Life, and pass it as legislation in chapter by the 2nd chapter of their term, containing the following:
      i. A plan for the creation of Scholarship contracts for all brothers.
      i. A plan for ensuring the chapter house is an environment conducive to studying.
      i. A plan for providing incentives for academic achievements.
   a. Will present the scholarship program to new members.
   a. Works with the Marshal to promote academic well-being among New Members.
   a. Organizes a formal scholarship dinner to recognize achievement about scholarship within the chapter.
   a. Will arrange at least one program per semester with a speaker who will talk to the chapter about scholarship or an issue relating to scholarship.
   a. Will ensure all brothers are part of at least one non-greek club or activity.
   a. {{< var glossary.attend >}}s monthly meetings with the Greek Community Educational Consultants in accordance with Case Western Reserve University ({{< var acronyms.cwru >}}) Greek {{< var glossary.community-standards >}}.
   a. Serves as a member of {{< var acronyms.ec >}}.
   a. Must live in the house.

@@

1. Historian
   a. Performs all duties stated in the I{{< var acronyms.ibl >}}BL Article V, Section 6, paragraph h.
   a. Assists alumni relations chair with the alumni database.
   a. Ensures that pictures are taken at chapter events.
   a. Will make a yearly scrapbook for the year that they serve, with assistance from the previous historian.
   a. Manages the chapter's online photo and video galleries jointly with the Public Relations Chair.
   a. Works with the house manager to ensure that composites are displayed correctly.
   a. Maintains and updates the photos around the house.
   a. Maintains the chapter museum.

@@

1. Alumni Relations Chair
   a. Collects materials for and edits the Alumni Newsletter with the help of the Alumni Corporation and sends out the Alumni newsletter before the last day of classes.
   a. Maintains the alumni database.
   a. Serves as chair of the Alumni Relations Committee.
   a. Organizes the Alumni Ceremony at the end of the semester in which they serve.
   a. Plans the annual OX Roast event with the alumni to be held in the fall semester.
   a. Will be appointed after OX Roast to serve until the next OX Roast.
   a. Serves as a member of {{< var acronyms.ccc >}}.

@@

1. Food Steward
   a. Works with a chef or catering service to maintain a brotherhood meal plan.
   a. Ensures the service chosen for the meal plan is paid for according to the agreement with the chef or catering service.
   a. Must be on the meal plan.
   a. Works with the Detail Manager to keep public areas in the kitchen clean and ensure proper storage of food.
   a. Assigns cabinet and fridge space to in-house brothers.
   a. Must live in the house.

@@

1. Voting
   a. Voting Members
      i. Vice President
      i. Vice President of Health and Safety
      i. Secretary
      i. Treasurer
      i. Marshal
      i. Recruitment Chair
      i. Scholarship Chair
   a. {{< var glossary.quorum >}} will consist of at least five members, at least four of whom must be voting members. c. All votes are decided by an {{< var glossary.absolute-majority >}} of {{< var acronyms.ec >}}.
      i. The President will have a vote in case of a tie.

@@

1. The chapter will have the following groups of committees:
   a. Standard Committees
      i. Each Standard committee is part of a committee pair. The list of committees and committee pairs is as follows:
         1. Alumni Relations Committee and Member Development Committee
         1. Health and Safety Committee and Scholarship Committee
         1. Philanthropy and Service Committee and Social Committee
         1. Public Relations Committee and Recruitment Committee
      i. All Standard committees will do the following:
         1. Meet at least once every two weeks as directed by their chair.
            a. In direct exception to the previous bylaw, the Alumni Relations Committee and Member Development Committee only need to meet at least once every four weeks as directed by their chair.
         1. Assist the chair in the discharge of their duties.
         1. Create a set of goals for the committee at the first meeting of the committee.
         1. Work toward the goals of the committee.
   b. Operational Committees
      i. Ad hoc committees
         1. The Vice President has the power to make other committees at their discretion.
      i. Budget Committee
         1. Purpose and Duties
            a. To create a budget for the chapter for the next year pursuant to @sec-art-GD7C1K2U.
            a. To examine any financial issues of the chapter.
         1. Membership
            a. The Treasurer will serve as chair of the Budget Committee.
            a. The body of the committee will be selected by the Treasurer.
         1. Procedure
            a. The committee will be created and convened during the budgeting process outlined in @sec-art-GD7C1K2U, Item 3.
            a. The committee may meet at other times to examine the finances of the chapter at the direction of {{< var acronyms.ec >}}.
      i. Committee Chair Committee ({{< var acronyms.ccc >}})
         1. Purpose
            a. To facilitate communication between committee chairs.
            a. To keep the Vice President informed of committee business.
            a. To help the Vice President ensure that committees are performing all necessary duties.
         1. Membership
            a. The Vice President will serve as the chair of {{< var acronyms.ccc >}}.
            a. The chairs of all Standard Committees will be members.
            a. Other brothers may be added to {{< var acronyms.ccc >}} at the Vice President's discretion.
         1. Procedure
            a. The committee will meet at least once every two weeks while school is in session.
            a. The Vice President will evaluate progress toward committee goals.
      i. Mandatory Bylaw Revision Committee
         1. The Mandatory Bylaw Revision Committee will function in accordance with @sec-art-YOSPIQLS.
